Bare Demo of IEEEtran.cls for Journals

### 2019-12-22 3-UHD/report/paper.tex
update fake image generation

\section{Related Work}
% lcx
\section{Subsampling and Interpolation}

\subsection{Subsampling}
Resampling using pixel area relation. Suppose $x\times y$ image subsampled down to size $x'\times y'$. scale\_x = x/x', scale\_y = y/y', and then we get block $scale\_x \times scale\_y$, block\_area = $scale\_x \times scale\_y$, the new image's each pixel is the weighted average of pixels in corresponding block's of the original image: 
\begin{align*}
	p'(x',y')=\sum_{i,j}{\frac{covered\_area \cdot p(i,j)}{block\_area}}
\end{align*}
i,j are nonnegative integers, $i \in [scale\_x\times x,scale\_x\times (x+1)]$ $j \in [scale\_y\times y,scale\_y\times (y+1)]$

\subsection{Interpolation}
In the mathematical field of numerical analysis, interpolation is a type of estimation, a method of constructing new data points within the range of a discrete set of known data points. In this project we use bilinear interpolation, bicubic interpolation, Lanczos resampling.

\subsubsection{Bilinear Interpolation}
\begin{figure}[h]
	\centering
	\includegraphics[width=0.6\linewidth]{fig/1.png}
	\label{fig:Bilinear Interpolation}
\end{figure}
\par First do linear interpolation in the x-direction:
\begin{align*}
p(R_1) = \frac{x_2-x}{x_2-x_1}\cdot p(Q_{11})+\frac{x-x_1}{x_2-x_1}\cdot p(Q_{21})\\
p(R_2) = \frac{x_2-x}{x_2-x_1}\cdot p(Q_{12})+\frac{x-x_1}{x_2-x_1}\cdot p(Q_{22})
\end{align*}
Then interpolate in the y-direction:
\begin{align*}
p(P) &= \frac{y2-y}{y2-y1}\cdot p(R_1)+\frac{y-y1}{y2-y1}\cdot p(R_2)\\ &=\small{\frac {1}{(x_{2}-x_{1})(y_{2}-y_{1})}}{\begin{bmatrix}x_{2}-x&x-x_{1}\end{bmatrix}}{\begin{bmatrix}f(Q_{11})&f(Q_{12})\\f(Q_{21})&f(Q_{22})\end{bmatrix}}{\begin{bmatrix}y_{2}-y\\y-y_{1}\end{bmatrix}}
\end{align*}
\par We can get the corresponding pixel's coordinate in original image: $x'\cdot scale\_x=x$, $y'\cdot scale\_y=y$. If either x or y is not integer, $x_1=int(x),x_2=int(x)+1,y_1=int(y), y_2=int(y)+1$, do interpolation.
\par This algorithm reduces some of the visual distortion caused by resizing an image to a non-integral zoom factor.
~\\
\subsubsection{Bicubic Interpolation}
~\\
\par In this method, new image’s pixel at point (x', y'), p(x',y'), is the weighted average of the nearest 16 points in the original image. An interpolator can be obtained by applying a convolution with the following kernel in both dimensions:
\begin{align*}
{\displaystyle W(x)={\begin{cases}(a+2)|x|^{3}-(a+3)|x|^{2}+1&{\text{for }}|x|\leq 1,\\a|x|^{3}-5a|x|^{2}+8a|x|-4a&{\text{for }}1<|x|<2,\\0&{\text{otherwise}},\end{cases}}}
\end{align*}
where a is usually set to −0.5 or −0.75.
\par $x'\cdot scale\_x=x$, $y'\cdot scale\_y=y$. If either x or y is not integer, $x_i$=int(x+i), $y_j$=int(y+j), i, j = -1,0,1,2:

@@

@@

We can do this by first subsampling a given image, then using every know algorithm to upsampling the downsampled image back to the original size.
Say the image is originally faked with algorithm A, then the reconstructed image using algorithm A should result in very small MSE wrt. to the original one.
If after enumerated all possible algorithms and subsampling rate (also assumed limited), no algorithm satisfy the above statement, then we can assert that the image is UHD.

@@

However, we can still refer to the idea of reconstruct a reference image by first subsampling then upsampling with some reference interpolation method.
If we use the most trivial interpolation method to generate the reference, for any given image, the more it improves from the reference, we are more confident that it is true UHD.
This idea gives birth to the relative DCT analysis we propose later.

@@

Another idea is that, there are always noises in real UHD images due to the inherent deficiencies in equipments, whereas the fake UHD images undergoes a stage of subsampling, which eliminates some noises.
As a result, the fake UHD image should be more smooth than the original one.
We can use DCT to extract the magnitudes at different frequencies, and observe those for high frequencies is relatively lower in fake UHD images.

>>>>

\section{Related Work}
% lcx
\section{Fake Image Generation}

\subsection{Downsampling}
We first construct 1080P and 720P images using downsampling according to pixel area relation. Suppose $x\times y$ image downsampled down to size $x'\times y'$. scale\_x = x/x', scale\_y = y/y', and then we get block $scale\_x \times scale\_y$, block\_area = $scale\_x \times scale\_y$, the new image's each pixel is the weighted average of pixels in corresponding block's of the original image: 
\begin{align*}
	p'(x',y')=\sum_{i,j}{\frac{covered\_area \cdot p(i,j)}{block\_area}}
\end{align*}
i,j are nonnegative integers, $i \in [scale\_x\times x,scale\_x\times (x+1)]$ $j \in [scale\_y\times y,scale\_y\times (y+1)]$

\subsection{Interpolation}
The next step to construct fake images is to upsample those downsampled images back to 4K defintion.
In the mathematical field of numerical analysis, interpolation is a type of estimation, a method of constructing new data points within the range of a discrete set of known data points.
In this project we use bilinear interpolation, bicubic interpolation, Lanczos interpolation to generate fake images.

\subsubsection{Bilinear Interpolation}
\par First do linear interpolation in the x-direction:
\begin{align*}
p(R_1) = \frac{x_2-x}{x_2-x_1}\cdot p(Q_{11})+\frac{x-x_1}{x_2-x_1}\cdot p(Q_{21})\\
p(R_2) = \frac{x_2-x}{x_2-x_1}\cdot p(Q_{12})+\frac{x-x_1}{x_2-x_1}\cdot p(Q_{22})
\end{align*}
Then interpolate in the y-direction:
\begin{align*}
p(P) &= \frac{y2-y}{y2-y1}\cdot p(R_1)+\frac{y-y1}{y2-y1}\cdot p(R_2)\\ &=\small{\frac {1}{(x_{2}-x_{1})(y_{2}-y_{1})}} F {\begin{bmatrix}y_{2}-y\\y-y_{1}\end{bmatrix}} \\
& \text{where } F = {\begin{bmatrix}x_{2}-x&x-x_{1}\end{bmatrix}}{\begin{bmatrix}f(Q_{11})&f(Q_{12})\\f(Q_{21})&f(Q_{22})\end{bmatrix}}
\end{align*}
\par We can get the corresponding pixel's coordinate in original image: $x'\cdot scale\_x=x$, $y'\cdot scale\_y=y$. If either x or y is not integer, $x_1=int(x),x_2=int(x)+1,y_1=int(y), y_2=int(y)+1$, do interpolation.
\par This algorithm reduces some of the visual distortion caused by resizing an image to a non-integral zoom factor.
~\\
\subsubsection{Bicubic Interpolation}
~\\
\par In this method, new image’s pixel at point (x', y'), p(x',y'), is the weighted average of the nearest 16 points in the original image. An interpolator can be obtained by applying a convolution with the following kernel in both dimensions:
\begin{align*}
{\displaystyle W(x)={\begin{cases}(a+2)|x|^{3}-(a+3)|x|^{2}+1&{\text{for }}|x|\leq 1,\\a|x|^{3}-5a|x|^{2}+8a|x|-4a&{\text{for }}1<|x|<2,\\0&{\text{otherwise}},\end{cases}}}
\end{align*}
where a is usually set to −0.5 or −0.75.
\par $x'\cdot scale\_x=x$, $y'\cdot scale\_y=y$. If either x or y is not integer, $x_i$=int(x+i), $y_j$=int(y+j), i, j = -1,0,1,2:

@@

Now we have 6 different categories of 1200 fake UHD images versus 200 real UHD images.
Notice that we have not used DNN models for generating fake UHD images, which will be later used to examine our models.
We then start developing models to distinguish real ones from fake ones.

@@

We can do this by first downsampling a given image, then using every know algorithm to upsampling the downsampled image back to the original size.
Say the image is originally faked with algorithm A, then the reconstructed image using algorithm A should result in very small MSE wrt. to the original one.
If after enumerated all possible algorithms and downsampling rate (also assumed limited), no algorithm satisfy the above statement, then we can assert that the image is UHD.

@@

However, we can still refer to the idea of reconstruct a reference image by first downsampling then upsampling with some reference interpolation method.
If we use the most trivial interpolation method to generate the reference, for any given image, the more it improves from the reference, we are more confident that it is true UHD.
This idea gives birth to the relative DCT analysis we propose later.

@@

Another idea is that, there are always noises in real UHD images due to the inherent deficiencies in equipments, whereas the fake UHD images undergoes a stage of downsampling, which eliminates some noises.
As a result, the fake UHD image should be more smooth than the original one.
We can use DCT to extract the magnitudes at different frequencies, and observe those for high frequencies is relatively lower in fake UHD images.
